---
title: "Indicadores"
date: "20/1/2021"
output: html_document
---
#1. Cargar librerias
```{r librerias y configuracion, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.align = "center")
library(tidyverse)

```

Leer base de datos
```{r}
SECOP_I <- read_delim("secop_i_ips_limpia.csv", ";", 
                      escape_double = FALSE, trim_ws = TRUE)
```
nombre_entidad	nit_entidad	orden_entidad	departamento_entidad	municipio_entidad
total_contratos	valor_total	valor_mediana	valor_promedio	valor_desviacion	perc_adic_valor	perc_adic_tiempo	perc_contr_directa_num	perc_contr_direct_val	HHI_cant	HHI_val	ID_cant	ID_val	ganadoras	IC4K_cant	IC4K_val	ind_riesgo_corrupcion

Seleccionar Columnas
```{r cargar datos}
# Cargar datos
contratos <- SECOP_I %>% select(nombre_entidad, tipo_proceso, tipo_contrato,                                                                           cuantia_contrato, id_contratista,
                                   objeto_contratar, detalle_objeto_contratar, ruta_web)
#distinct()

```

